The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-17 writing/draft3/draft13.tex
asdf

 allowed for both are moving and adding 
model building approach using  To be more specific, we started with a model which included the complete set of our weather measures in both fixed effects and random effects. In the following steps, the insignificant random effects and subsequently insignificant fixed effects were removed one by one until only significant predictors remained. For random effects we considered the level of significance $\alpha=0.1$ and for fixed effects we opted for $\alpha=0.05$~\cite{lmerTest}.

\textcolor{blue}{the Satterthwaite's method to determine the p-values of the individual t-tests} \cite{lmerTest}
	\section{Results}\label{Results}

>>>>

To verify our results, we adapted an alternative step-down model building
approach using the Satterthwaite’s method to determine the p-values of the individual
t-tests \cite{lmerTest}. To be more specific, we started with a model which included the complete set of our weather measures in both fixed effects and random effects. In the first part of this procedure the insignificant random effects were removed one by one until only significant predictors remained. After this, the insignificant fixed effects were removed one by one until only significant predictors remained. For random effects we considered the level of significance $\alpha=0.1$ and for fixed effects we opted for $\alpha=0.05$~\cite{lmerTest}. Using this method we chose the same model as according to the AIC-based stepwise method described above.

	\section{Results}\label{Results}
